What can GitHub and Googlecode Issues tell us about Exceptions in Android and Java?

### 2014-08-31 android-stacks.tex
adding more data on google code

\title{ What can GitHub and Googlecode Issues tell us about Exceptions in Android? }

@@

This paper reports a repository mining study which analyzed all the issues created on
Android projects available in GitHub (482 applications) and Google code (141 applications)
Overall, our research set includes XXXX issues from which XXX stack traces 
were extracted. Such stack traces were distilled and analyzed in 
combination with source code and bytecode analysis. This study 
consistently identifies common characteristics of reported 
exception stacks traces - e.g., the NullPointerException was the reported cause 
on 30,08\% of all analyzed exception stack traces, and was mentioned in approximately 
50\% of all projects analyzed. Moreover,  the cross-project analysis 
of exception stack traces enabled to consistently reveal   
fragilities of exception handling code: 
(1) undocumented runtime exceptions signaled by third party code,
(2) undocumented checked exceptions thrown by Android native code
(3) unexpected exception wrappings (e.g., Errors being wrapped in checked exceptions) 
revealing that Java hybrid exception model is not fully used according to its purpose.
Such fragilities impose challenges to application robustness not only 
in Android environment but also to other systems based on Java exception model.

@@

To identify Android projects in Googlecode, we performed a similar heuristic, we performed a case insensitive search 
(on Googlecode search interface) for the term \textsf{android}.  On January 2014, when we queried Googlecode, such heuristic could
 find 788  projects, from which 724 defined at least 1 issue and, 183 projects 
had at least one issue including a stack trace. Then we performed further cleanup, inspecting the site of every Android
reporting at least one stack trace, and as a result we could identify 158 
Android projects.

@@

\subsection{The Common Root Exceptions and What They can Tell us? }

After distilling the information available on the exception stack traces we could find 
the the exceptions commonly reported as the root causes of stack traces.
Table \ref{tab:toptenandroid} illustrates the top 10 root causes found in the study,
 ranked by the number of distinct project repositories on which they were reported. 
The table shows: the number of times each exception was reported as 
the root cause of a stack trace, the number of distinct projects reporting such causes on stack traces, 
and the percentages of such in relation to all reported exceptions and analyzed projects respectively.
It also presents the whether the method responsible for signaling the exceptions were
part of Android, the application itself, libcore, or a third-party library as presented in Table  \ref{tab:signalers} 
 \footnote{9 stack traces contained only elements of JVM and were discarded from the analysis}.

@@

\begin{table*}
  \centering
  \begin{tabular}{rcccccccc}
    \hline
    \bfseries{Root Exception} &  \multicolumn{2}{c}{\bfseries{Projects}} &  \multicolumn{2}{c}{\bfseries{Occurrences}} & \textsf{Android} & \textsf{Libcore} & \textsf{App} & \textsf{Lib} \\
    & \bfseries{\#} &  \bfseries{\%} & \bfseries{\# } & \bfseries{\% } &&&&\\
    \hline
java.lang.NullPointerException            & 254 & 52,70\%  & 1225 & 30,08\% & 473 & 18 & 595 & 137 \\
java.lang.IllegalStateException          & 99  & 20,54\%  & 234  & 5,75\%  & 165 & 12 & 36  & 20  \\
java.lang.IllegalArgumentException          & 94  & 19,50\% & 255  & 6,26\% & 146 & 6  & 64  & 39   \\
java.lang.RuntimeException                & 91  & 18,88\% & 232  & 5,70\%  & 167 & 1  & 47  & 17   \\
java.lang.OutOfMemoryError                 & 56  & 11,62\% & 180  & 4,42\% & 121 & 15 & 17  & 23   \\
java.lang.NoClassDefFoundError           & 52  & 10,79\%  & 73   & 1,79\%  & 9   & 0  & 37  & 26   \\
java.lang.ClassCastException             & 49  & 10,17\%  & 94   & 2,31\%  & 43  & 0  & 40  & 11   \\
java.lang.IndexOutOfBoundsException       & 47  & 9,75\%   & 127  & 3,12\% & 47  & 0  & 71  & 8    \\
java.lang.NoSuchMethodError               & 40  & 8,30\%  & 57   & 1,40\%  & 9   & 0  & 39  & 9   \\
java.util.ConcurrentModificationException & 38  & 7,88\% & 54   & 1,33\%   & 5   & 0  & 43  & 6   \\

@@

\begin{table}
  \centering
  \begin{tabular}{lrr}
    \hline
    \bfseries{Category} &  \bfseries{Occurence on Stacks (\%)} \\
    \hline
      Programming logic (java.lang and util) & 2326 (57,9\%)\\
      Resources (IO)                         &  727 (18,1\%) \\
      Security                               &  165 (4,1\%)\\
      Concurrency                            & 116  (2,9\%)\\
      Backward compatibility                 &  219 (5,5\%) \\
      Specific Exceptions               &  197 (4,9\%)\\
      General (Error, Exception, Runtime)    &  267 (6,7\%)\\
    \hline
  \end{tabular}
  \caption{Characterization of the 100 root causes.}
  \label{tab:tophundrend}
\end{table}

@@

In this second analysis the programming mistakes were also the
most mentioned root causes, followed by exceptions related to resource 
management (which was expected since on mobile environment 
resources are usually scarce). We could observe that there were 
stack traces related to the main concerns of mobile develoment.

@@

\subsection{What the Cross-Type  Exception Wrappings can Tell us?}

\subsection{Exploring the Information Embedded on Exception Wrappings}
Table~\ref{tab:wrappingandroid} presents the wrappings found in this study for all
stack traces found in Android repositories. As we can see, some of the checked
exceptions were indeed wrapped in runtime exceptions or even errors.

@@

\begin{table}
\centering
\begin{tabular}{lll}
 \bfseries{Signaler class} &  \bfseries{Wrapper Type} & \bfseries{Ocurrences} \\
    \hline
android.app.ActivityThread & java.lang.RuntimeException & 47 \\
android.view.LayoutInflater & android.view.InflateException &  7 \\
android.os.AsyncTask & java.lang.RuntimeException &  5 \\
Other platform classes & java.lang.RuntimeException &   7 \\
\hline
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{ll}
 \bfseries{Wrapper type - Root cause type} & \bfseries{Ocurrences} \\
    \hline
java.lang.RuntimeException - java.lang.OutOfMemoryError & 30\\
java.lang.RuntimeException - java.lang.NoClassDefFoundError & 6\\
java.lang.RuntimeException - java.lang.UnsatisfiedLinkError) & 5\\
java.lang.RuntimeException -  java.lang.StackOverflowError)  & 4\\
\hline
  \end{tabular}
\caption{Elements responsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{lll}
 \bfseries{Wrapper} & \bfseries{Root} & \bfseries{Ocurrences}\\
 \hline
...android.robospice.CacheSavingException - java.lang.ClassCastException & 6 \\
java.lang.reflect.InvocationTargetException - java.lang.NullPointerException &  3 \\
java.lang.reflect.InvocationTargetException - android...ResourcesdNotFoundException & 2 \\
java.sql.SQLException,android.database.sqlite.SQLiteDiskIOException & 2 \\
java.lang.Exception,at.andiwand.odf2html.odf.IllegalMimeTypeException & 	2 \\
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{lll}
 \bfseries{Wrapper} & \bfseries{Root} & \bfseries{Ocurrences}\\
 \hline
java.lang.reflect.InvocationTargetException,java.lang.OutOfMemoryError & 5 \\
java.lang.Exception,java.lang.OutOfMemoryError & 1 \\
java.lang.reflect.InvocationTargetException,java.lang.NoSuchMethodError &	1 \\
java.lang.reflect.InvocationTargetException,java.lang.UnsatisfiedLinkError&	1 \\
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapcheckerr}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{lll}
 \bfseries{Wrapper} & \bfseries{Root} & \bfseries{Ocurrences}\\
 \hline
java.lang.NoClassDefFoundError & java.lang.ClassNotFoundException & 4 \\
java.lang.AssertionError & javax.crypto.ShortBufferException) & 3 \\
 \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{lll}
 \bfseries{Wrapper} & \bfseries{Root} & \bfseries{Ocurrences}\\
 \hline
java.lang.ExceptionInInitializerError,java.lang.NullPointerException & 9 \\
java.lang.ExceptionInInitializerError,java.lang.IllegalArgumentException &	2 \\
java.lang.ExceptionInInitializerError,java.util.MissingResourceException) &	1 \\
java.lang.ExceptionInInitializerError,org.andengine.util.exception.AndEngineRuntimeException &	1 \\
 \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

\section{Discussions and Actionable Advices}

The results of this study sheds light on 
problems that may be reducing the robustness of current Java programs in the face of
exceptional conditions.

\subsection{Cross-Type Wrappings and Threats to Dependability}
The cross-type wrappings detected in this study points to the fact that: (1) exception 
wrappings may prevent exception types from being used according to its initial purpose
 (e.g, Errors should represent situations that should not be handled); and (2) may  be used
 to bypass the language restrictions imposed by checked exceptions  (e.g,
 checked exceptions may be wrapped in runtime exceptions).

\begin{figure} \centering \includegraphics[scale=0.4]{codeexample2.pdf}
\caption{Code snipets illustrating fragilities on the exception handling code} \label{fig:exchier} \end{figure}

Hence, when (mis)applied, the exception wrapping can make the exception handling code
 more complex and lead to what we call an \emph{exception handling confusion problem} which can lead the program to
an unpredictable state in the presence of exceptions. To illustrate this problem, we can use
 one of the examples found in this study: when the developer is 
confronted with a checked exception, the designer of the API is telling him 
to handle the exceptional condition, however we could observe that in some cases the 
checked exception wrapped an OutOfMemoryError, which represent resource deficiency detected 
by the JVM which make impossible the program to recover.

@@

\subsection{The Almost Infeasible Task of Preventing Uncaught Exceptions}

In this study we could observe undocumented runtime exceptions thrown by third party code,
and even undocumented checked exception thrown by Java supporting library.
Such undocumented exceptions make difficult, and most of the times infeasible
for the client code to protect against "unforeseen" situations that may happen 
while calling a library code.

@@

\subsection{The high number of NullPointerExceptions}

@@

The high number of null pointer exceptions found in this mining study shed light into a problem
that although known was not supported by large scale mining studies.

@@

\subsection{General Solution: a General Handler?}
One may think that the solution for the uncaught exceptions that lead to the system crash,
is to define a general handler, which is responsible for handling any exception that is not
adequately handled inside the applications. Although this solution may prevent 
the system of abruptly crashing, such general handler will not have enough
contextual information to adequately handle the exception, 
and the main recovery task will be to present a message to the user
 and restart the application.

@@

\subsection{The benefits of a cross-project crash analysis}

@@

Using exception miner tool we could identify the methods responsible for most of the crashes - 
such methods can be a target for manual inspections improvements, or better documentation
(because sometimes an exception can be thrown because the user is not invoking the method
in the proper way

During such analysis we could also find the undocumented runtime exceptions 
signaled by libraries.

>>>>

\title{ What can GitHub and Googlecode Issues tell us about Exceptions in Android and Java? }

@@

This paper reports a repository mining study which analyzed all the issues created on
Android projects available in GitHub (482 applications) and Google code (157 applications)
Overall, our research set includes 32,582 issues in GitHub and 41,674 issues in Googlecode from which (4,208)  (1,986) in GC stack traces 
were extracted. Such stack traces were distilled and analyzed in 
combination with source code and bytecode analysis. This study 
consistently identifies common characteristics of reported 
exception stacks traces - e.g., the NullPointerException was the reported cause 
on 30,08\% of all analyzed exception stack traces, and was mentioned in approximately 
50\% of all projects analyzed. Moreover,  the cross-project analysis 
of exception stack traces enabled to consistently reveal   
fragilities of exception handling code: 
(1) undocumented runtime exceptions signaled by third party code,
(2) undocumented checked exceptions thrown by Android native code
(3) unexpected exception wrappings (e.g., Errors being wrapped in checked exceptions) 
revealing that Java hybrid exception model is not fully used according to its purpose.
Such fragilities impose challenges to application robustness not only 
in Android environment but also to other systems based on Java exception model.

@@

To identify Android projects in Googlecode, we performed a similar heuristic, we performed a case insensitive search 
(on Googlecode search interface) for the term \textsf{android}.  On January 2014, when we queried Googlecode, such heuristic could
 find 788  projects, from which 724 defined at least 1 issue and, 183 projects 
had at least one issue including a stack trace. Then we performed further cleanup, inspecting the site of every Android
reporting at least one stack trace, and as a result we could identify 157. 
Android projects.  From this set all issues (41,674) were analyzed and 1,986 stack traces were extracted.

@@

\subsection{What the Common Root Exceptions can tell us? }

After distilling the information available on the exception stack traces we could find 
the the exceptions commonly reported as the root causes of stack traces.
Table \ref{tab:toptenandroid} illustrates the top 10 root causes found in the study,
 ranked by the number of distinct project repositories on which they were reported. 
The table shows: the number of times each exception was reported as 
the root cause of a stack trace, the number of distinct projects reporting such causes on stack traces, 
and the percentages of such in relation to all reported exceptions and analyzed projects respectively.
It also presents the whether the method responsible for signaling the exceptions were
part of Android, the application itself, libcore, or a third-party library as presented in Table  \ref{tab:signalers} 
 \footnote{Nine exception stack traces contained only elements of JVM and were discarded from the analysis}.

@@

\begin{table*}
  \centering
  \begin{tabular}{rcccccccc}
    \hline
    \bfseries{Root Exception} &  \multicolumn{2}{c}{\bfseries{Projects (GH/CG)}} &  \multicolumn{2}{c}{\bfseries{Occurrences (GH/CG)}} & \textsf{Android} & \textsf{Libcore} & \textsf{App} & \textsf{Lib} \\
    & \bfseries{\#} &  \bfseries{\%} & \bfseries{\# } & \bfseries{\% } &&&&\\
    \hline
java.lang.NullPointerException            & 254 /  78  & 52,70\%  & 1225 / 439  & 30,08\% & 473 /  26  & 18 & 595 & 137 \\  %LIBORAPP=408
java.lang.IllegalStateException          & 99 / 21  & 20,54\%  & 234 / 44  & 5,75\%  & 165 & 12 & 36  & 20  \\
java.lang.IllegalArgumentException          & 94 / 48  & 19,50\% & 255 / 98  & 6,26\% & 146 & 6  & 64  & 39   \\
java.lang.RuntimeException                & 91 / 31 & 18,88\% & 232 / 87  & 5,70\%  & 167 & 1  & 47  & 17   \\
java.lang.OutOfMemoryError                 & 56  / 22  & 11,62\% & 180 / 57 & 4,42\% & 121 & 15 & 17  & 23   \\
java.lang.NoClassDefFoundError           & 52  / 15 & 10,79\%  & 73 / 21   & 1,79\%  & 9   & 0  & 37  & 26   \\
java.lang.ClassCastException             & 49  / 15 & 10,17\%  & 94 / 36   & 2,31\%  & 43  & 0  & 40  & 11   \\
java.lang.IndexOutOfBoundsException       & 47  / 15 & 9,75\%   & 127 / 39  & 3,12\% & 47  & 0  & 71  & 8    \\
java.lang.NoSuchMethodError               & 40 / 14  & 8,30\%  & 57 / 23  & 1,40\%  & 9   & 0  & 39  & 9   \\
java.util.ConcurrentModificationException & 38 / 5 & 7,88\% & 54 / 11  & 1,33\%   & 5   & 0  & 43  & 6   \\

@@

\begin{table}
  \centering
  \begin{tabular}{lrr}
    \hline
    \bfseries{Category} &  \bfseries{\% reported on stacks} \\
    \hline
      Programming logic (java.lang and util) &  57,9\%\\ %2326
      Resources (IO)                         &   18,1\% \\ %727
      Security                               &  4,1\%\\ %165 
      Concurrency                            &  2,9\% \\ %116 
      Backward compatibility                 & 5,5\% \\ %219
      Specific Exceptions               &  4,9\%\\ %197 
      General (Error, Exception, Runtime)    &  6,7\%\\ %267 
    \hline
  \end{tabular}
  \caption{Characterization of the 100 root causes.}
  \label{tab:tophundrend}
\end{table}

@@

In this second analysis the programming mistakes were also the
most mentioned root causes, followed by exceptions related to resource 
management (which was expected since on mobile environment 
resources are usually scarce). Some of such programming mistakes,
however, may be interactly related to one of the other concerns. For 
instance, a concurrency problem may lead to a NullPointerException.
This classification however, was only based on the semantic embedded 
on the exception types.

@@

\subsection{What the Exception Wrappings can tell us?}
%\subsection{Exploring the Information Embedded on Exception Wrappings}
Table~\ref{tab:wrappingandroid} presents the wrappings found in this study for all
stack traces found in Android repositories. As we can see, some of the checked
exceptions were indeed wrapped in runtime exceptions or even errors.

@@

\begin{table}
\centering
\begin{tabular}{lll}
    \hline
 \bfseries{Signaler class} &  \bfseries{Wrapper Type} & \bfseries{Ocurrences} \\
    \hline
android.app.ActivityThread & java.lang.RuntimeException & 47 \\
android.view.LayoutInflater & android.view.InflateException &  7 \\
android.os.AsyncTask & java.lang.RuntimeException &  5 \\
Other platform classes & java.lang.RuntimeException &   7 \\
\hline
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

%\begin{table}
%\centering
%\begin{tabular}{ll}
% \bfseries{Wrapper type - Root cause type} & \bfseries{\#} \\
%    \hline
%java.lang.RuntimeException - java.lang.OutOfMemoryError & 30\\
%java.lang.RuntimeException - java.lang.NoClassDefFoundError & 6\\
%java.lang.RuntimeException - java.lang.UnsatisfiedLinkError) & 5\\
%java.lang.RuntimeException -  java.lang.StackOverflowError)  & 4\\
%\hline
%  \end{tabular}
%\caption{Elements responsible for the wrapping.}
%\label{tab:wrapping01}
%\end{table}

\begin{table}
\centering

  \begin{tabular}{|p{7.9cm} p{0.1cm}|}
%\begin{tabular}{ll}
    \hline
 \bfseries{Runtime-Error Wrapping Examples} &   \\  %\bfseries{\#}
    \hline
java.lang.RuntimeException - java.lang.OutOfMemoryError & \\ %30
java.lang.RuntimeException - java.lang.NoClassDefFoundError &\\ %6
java.lang.RuntimeException - java.lang.UnsatisfiedLinkError) & \\ %5
java.lang.RuntimeException -  java.lang.StackOverflowError)  & \\ %4
\hline
\bfseries{Checked-Runtime Wrapping Examples} &  \\
 \hline
...android.robospice.CacheSavingException - java.lang.ClassCastException &  \\ %6
java.lang.reflect.InvocationTargetException - java.lang.NullPointerException &   \\ %3
java.lang.reflect.InvocationTargetException - ...ResourcesdNotFoundException &  \\ %2
java.sql.SQLException - android.database.sqlite.SQLiteDiskIOException &  \\ %2
 \hline
\bfseries{Checked-Error Wrapping Examples} & \\
 \hline
java.lang.reflect.InvocationTargetException - java.lang.OutOfMemoryError &  \\ %5
java.lang.Exception - java.lang.OutOfMemoryError &  \\ %1
java.lang.reflect.InvocationTargetException - java.lang.NoSuchMethodError &	 \\ %1
java.lang.reflect.InvocationTargetException - java.lang.UnsatisfiedLinkError&	 \\ %1
\hline
\bfseries{Error-Checked Wrapping Examples} & \\
 \hline
java.lang.NoClassDefFoundError - java.lang.ClassNotFoundException &  \\ %4
java.lang.AssertionError - javax.crypto.ShortBufferException) &  \\ %3
\hline
\bfseries{Error-Runtime Wrapping Examples} &   \\
 \hline
java.lang.ExceptionInInitializerError - java.lang.NullPointerException &  \\ %9
java.lang.ExceptionInInitializerError - java.lang.IllegalArgumentException &	 \\ %2
 \hline
  \end{tabular}
\caption{Wrapping examples}
\label{tab:wrapping01}
\end{table}

@@

%\begin{table}
%\centering
%\begin{tabular}{ll}
% \bfseries{Wrapper type - Root cause type} & \bfseries{\#}\\
% \hline
%...android.robospice.CacheSavingException - java.lang.ClassCastException & 6 \\
%java.lang.reflect.InvocationTargetException - java.lang.NullPointerException &  3 \\
%java.lang.reflect.InvocationTargetException - ...ResourcesdNotFoundException & 2 \\
%java.sql.SQLException - android.database.sqlite.SQLiteDiskIOException & 2 \\
%  \end{tabular}
%\caption{Elements tresponsible for the wrapping.}
%\label{tab:wrapping01}
%\end{table}

@@

%\begin{table}
%\centering
%\begin{tabular}{lll}
% \bfseries{Wrapper type - Root cause type} & \bfseries{\#}\\
% \hline
%java.lang.reflect.InvocationTargetException - java.lang.OutOfMemoryError & 5 \\
%java.lang.Exception - java.lang.OutOfMemoryError & 1 \\
%java.lang.reflect.InvocationTargetException - java.lang.NoSuchMethodError &	1 \\
%java.lang.reflect.InvocationTargetException - java.lang.UnsatisfiedLinkError&	1 \\
%  \end{tabular}
%\caption{Elements tresponsible for the wrapping.}
%\label{tab:wrapcheckerr}
%\end{table}

@@

%\begin{table}
%\centering
%\begin{tabular}{lll}
% \bfseries{Wrapper} & \bfseries{Root} & \bfseries{\#}\\
% \hline
%java.lang.NoClassDefFoundError & java.lang.ClassNotFoundException & 4 \\
%java.lang.AssertionError & javax.crypto.ShortBufferException) & 3 \\
% \end{tabular}
%\caption{Elements tresponsible for the wrapping.}
%\label{tab:wrapping01}
%\end{table}

@@

%\begin{table}
%\centering
%\begin{tabular}{ll}
% \bfseries{Wrapper type - Root cause type} & \bfseries{\#} \\
% \hline
%java.lang.ExceptionInInitializerError - java.lang.NullPointerException & 9 \\
%java.lang.ExceptionInInitializerError - java.lang.IllegalArgumentException &	2 \\
% \end{tabular}
%\caption{Elements tresponsible for the wrapping.}
%\label{tab:wrapping01}
%\end{table}

@@

\section{Futher Discussions}

\begin{figure} \centering \includegraphics[scale=0.4]{codeexample2.pdf}
\caption{Code snippets illustrating fragilities on the exception handling code} \label{fig:exchier} \end{figure}

\emph{"Everybody hates thinking about exceptions,                   							because they’re not supposed to happen."}
\textbf{Brian Foote}

\subsection{On the cross-type wrappings as a threat to dependability}
The cross-type wrappings detected in this study points to the fact that: (1) exception 
wrappings may prevent exception types from being used according to its initial purpose
 (e.g, Errors should represent situations that should not be handled); and (2) may  be used
 to bypass the language restrictions imposed by checked exceptions  (e.g,
 checked exceptions may be wrapped in runtime exceptions).

Hence, when (mis)applied, the exception wrapping can make the exception handling code
 more complex and lead to what we call an \emph{exception handling confusion problem}.
Such problem can lead the program to
an unpredictable state in the presence of exceptions. To illustrate this problem, we can use
 one of the examples found in this study: when the developer is 
confronted with a checked exception, the designer of the API is telling him 
to handle the exceptional condition, however we could observe that in some cases the 
checked exception wrapped an OutOfMemoryError, which represent resource deficiency detected 
by the JVM which make impossible the program to recover.

@@

\subsection{On the need of a rescue to the almost Infeasible task of preventing uncaught exceptions}
In this study we could observe undocumented runtime exceptions thrown by third party code,
and even undocumented checked exception thrown by Java supporting library.
Such undocumented exceptions make difficult, and most of the times infeasible
for the client code to protect against "unforeseen" situations that may happen 
while calling a library code.

One may think that the solution for the uncaught exceptions 
may be to define a general handler, 
which is responsible for handling any exception that is not
adequately handled inside the applications. Although this 
solution may prevent  the system of abruptly crashing,
 such general handler will not have enough
contextual information to adequately handle the exception, 
and only tasks possible are: to present a message to the user
 and restart the application.

Such handler does not replace a carefully designed exception 
handling policy, which can hardly be designed in the absence of 
third-party documentation on the exceptions that
may the thrown by it.

@@

\subsection{On the Null Pointer Problem}

@@

The high number of null pointer exceptions found in this mining study shed light into a problem
that although known was not supported by large scale studies.

@@

@@

\subsection{On the benefits of a cross-project exception stack trace analysis}

@@

Using exception miner tool we could identify the methods responsible for most of the crashes - 
such methods can be a target for manual inspections improvements, or better documentation
(because sometimes an exception can be thrown because the user is not invoking the method
in the proper way ....

During such analysis we could also find the undocumented runtime exceptions 
signaled by reused therd part code libraries.
